### 2021-04-08 paper/ase21/overview.tex
[ASE21] Updated overview

\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
pair of a control point and its abstract environment from the worklist, produces
other pairs based on abstract semantics, and pushes them to the worklist.  The
iteration will be finished when the worklist becomes empty.

@@

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions (Section~\ref{sec:analysis}) and how to detect
type-related specification bugs using four different checkers
(Section~\ref{sec:checker}).  After we evaluate $\tool$
(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
and conclude (Section~\ref{sec:conclusion}).

>>>>

\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
pair of a control point and its abstract environment from the worklist, produces
other pairs based on abstract semantics, and pushes them to the worklist.  The
iteration will be finished when the worklist becomes empty.  Moreover, to reduce
false alarms by increasing the analysis precision, we perform refinement for
abstract environment when the current control point is a branch or an assertion.
The refinement will be described in detail in Section~\ref{sec:refine}.

@@

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase analysis precision using
refinement (Section~\ref{sec:analysis}) and how to detect type-related
specification bugs using four different checkers (Section~\ref{sec:checker}).
After we evaluate $\tool$ (Section~\ref{sec:eval}), we discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclusion}).
